---
title: "Calculate Csat (centrifuge data)"
subtitle: "Data = EC_sfpq276-598notag_CsatSN_data.csv"
author: "Andrew Marshall"
date: "05/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview:

This program:

1. Reads data collected using centrifuge method for protein saturation 
concentration determination. Converts supernatant A280 readings to [protein]. **

2. Plots supernatant [protein] over the total protein concentration.

3. Calculates saturation concentration (Csat) by taking mean supernatant [protein] 
of points with total [protein] greater than user-estimated Csat. **

4. Creates plots with horizontal line(s) to indicate Csat and data points as 
average +/- 95% CI.


\*\*Steps 1 and 3 require **user input**. 

### 1. Get data and calculate [protein]

```{r get data}
########################
### USER input: ########
   # protein extinction coefficient:
   extcoeff <- 0.454
   extcoeff_units <- "L/g"
   
   # protein molecular weight (Da):
   MW <- 38340.32
   
   # path to data (csv file):
   results_dir <- "\\\\uniwa.uwa.edu.au\\userhome\\staff7\\00101127\\My Documents\\LLPS results\\centrifuge_assays\\"
   results_data <- "EC_sfpq276-598notag_CsatSN_data.csv"
   
   # Include data from certain date(s) only?...
   date_of_experiment <- "na"
   # date_of_experiment <- "29.06.2022"
   
### (end user input) ###
########################
   
# Reads in data: 
df <- read.csv(paste(results_dir, results_data, sep = ""))

# Include data from certain date(s) only:
   if (date_of_experiment=="na"){
      df <- df
   } else {
      df <- df[df$date==date_of_experiment,]
   }
   
# Sort by KCl concentration and convert KCl_mM to factor:
df <- df[order(df$KCl_mM),]
df$KCl_mM <- as.factor(df$KCl_mM)

# Converts A280 to [protein] (micromolar):
sn_protein_gL <- df$A280/extcoeff
sn_protein_uM <- sn_protein_gL/MW*10^6
df$sn_protein_uM <- sn_protein_uM

```

### 2. Plot data
```{r}
library(ggplot2)

ggplot(data = df, mapping = aes(x = sample_uM, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point()
   # geom_smooth(method = "lm", formula = y ~ x+0) 
   # xlim(0, 35) +
   # ylim(0, 28)

```

### 3. Calculate Csat for each [KCl] and indicate on plot
```{r}
# Get all 500mM KCl data:
get500 <- df$KCl_mM == 500
df_500 <- df[get500,]

########################
### USER input: ########
   # For datapoints with sample_uM > estimated Csat, calculate average, SD and
   # 95% CI of sn_protein_uM value (grouped by [KCl]):
   estimated_Csat <- 400
   get150overCsat <- df$KCl_mM == 150 & df$sample_uM > estimated_Csat
   df_150overCsat <- df[get150overCsat,]
   N_observations <- as.numeric(nrow(df_150overCsat))
   Csat150 <- mean(df_150overCsat$sn_protein_uM)
   Csat150sd <- sd(df_150overCsat$sn_protein_uM)
   Csat150ci <- 1.96*(Csat150sd/sqrt(N_observations))
   
### (end user input) ###
########################

# library(dplyr)

ggplot(data = df, mapping = aes(x = sample_uM, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(data = df_500, method = "lm", formula = y ~ x+0, se = FALSE) +
   geom_hline(yintercept = Csat150, linetype = "dashed") +
   xlim(0, 1.1*max(df$sample_uM)) +
   ylim(0, 1.1*max(sn_protein_uM))

```

### 4. Create annotated plot with error bars: 
```{r}
# Collapse data to create new dataframe with mean and SD of observations
# (sn_protein_uM) grouped by KCl_uM + sample_uM:
library(doBy)

df_collapse <- summaryBy(sn_protein_uM ~ KCl_mM + sample_uM, 
                         data = df, 
                         FUN = c(length, mean, sd))
# Rename columns:
names(df_collapse)[names(df_collapse)=="sn_protein_uM.length"] <- "N"
names(df_collapse)[names(df_collapse)=="sn_protein_uM.mean"] <- "sn_protein_uM"
names(df_collapse)[names(df_collapse)=="sn_protein_uM.sd"] <- "sd"


# Convert Csat150 to string (for plot label):
Csat150chr <- paste(round(Csat150, digits = 1), "\u00b1", round(Csat150ci, digits = 1), "\u03bcM")

ggplot(data = df_collapse, mapping = aes(x = sample_uM, y = sn_protein_uM, group = KCl_mM)) +
   # labs(title = expression(SFPQ(WT)~italic(C)[sat]~by~centrifugation), caption = "Error bars are SD (n = 3). Csat uncertainty expressed as 95% CI.") +
   xlab("total [protein] (\u03bcM)") +
   ylab("supernatant [protein] (\u03bcM)") +
   # scale_x_continuous(expand = c(0, 0.0)) + 
   # scale_y_continuous(expand = c(0, 0.0)) +
   xlim(0, NA) +
   ylim(0, NA) +
   geom_point(aes(shape = KCl_mM), size = 1.5) +
   scale_shape_manual(values=c(1, 16),
                      name = "[KCl] (mM)") +
   geom_errorbar(aes(ymin=sn_protein_uM-sd, ymax=sn_protein_uM+sd), width=max(df$sample_uM*0.04)) +
   # geom_smooth(data = df_trunc2_500, method = "lm", formula = y ~ x+0, se = FALSE, colour = "black", size = 0.5) +
   geom_segment(aes(x = 0, xend = max(df$sample_uM), y = Csat150, yend = Csat150),
                linetype = "dashed",
                color = "darkred") +
   annotate(
      "text",
      x = max(df$sample_uM)*0.7,
      y = Csat150*0.05,
      size = 3,
      # label = as.expression(bquote(bold(bolditalic(C)[sat] == .(Csat150chr))))) +
      label = as.expression(bquote(bold(.(Csat150chr)))),
      color = "darkred") +
   theme_classic(base_size = 9) +
   theme(legend.key.size = unit(4, "mm"),
         legend.title = element_text(size = 7),
         legend.text = element_text(size = 7),
         legend.position = c(0.2,0.8),
         legend.background = element_blank(),
         aspect.ratio = 1,
         plot.caption = element_text(size = 5, colour = "darkgrey")
         )
```



### Save plot to file:
```{r}
ggsave(filename = paste(results_data, "_Rplot5x5_300.png"), 
       plot = last_plot(), 
       device = "png", 
       path = results_dir, 
       scale = 1,
       width = 5,
       height = 5,
       units = "cm",
       dpi = 300,
       limitsize = TRUE,
       bg = NULL)
```



### Conclusions...

