---
title: "Calculate Csat (fluorescence microscopy)"
subtitle: "Data = 20210716_sfpqQG (plateII rowH)"
author: "Andrew Marshall"
date: "16/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview:

This program:

1. Takes data from Drop_Counter.ijm **

2. Plots the total volume of condensed protein over the total protein concentration

3. Fits a straight line to points at [protein] > saturation concentration **

4. Calculates saturation concentration (Csat = x-intercept)

5. Calculates [protein] within condensed phase ** (*only accurate if contact angle has been measured accurately*)


\*\*Steps 1, 3 and 5 require *user input*. 

### 1. Get data:

```{r get data}
### USER input: ###
results_dir <- "\\\\uniwa.uwa.edu.au\\userhome\\staff7\\00101127\\My Documents\\LLPS results\\"
df <- read.csv(paste(results_dir, "20210716_sfpqQG\\plateII_H\\Method#2 (calculate total condensed volume)_CA30.csv", sep = ""))
```

### 2. Plot data:

```{r plot, echo=TRUE}
library(ggplot2)
ggplot(data = df, mapping = aes(x = Protein_Conc_uM, y = Cond_Vol_in_sample_nL)) +
   geom_point() +
   labs(title = "SFPQ(QG)-mEGFP 16/7/2021")
```

### 3/4 Do linear fit & calculate saturation concentration ('Csat'):

```{r}
### USER INPUT: ###
   # Write an estimate of the Csat here (only data points to the right of this will be used in linear fit):
   Csat_approx <- 1.75

   # Other points to exclude (e.g. outliers)?:
      #(must be a vector)
   excluded <- c(6)
### (end user input) ###

# Truncate results table to include only data > Csat and exclude any other user-specified points...
if (length(excluded) >= 1) {
   df_trunc <- df[-excluded,]
} else {
   df_trunc <- df
}
   
rows_to_keep <- df_trunc$Protein_Conc_uM > Csat_approx
df_trunc <- df_trunc[rows_to_keep,]


cond_vol <- df_trunc$Cond_Vol_in_sample_nL
prot_conc <- as.numeric(df_trunc$Protein_Conc_uM)

# (3) Do linear fit...
model_linear <- lm(cond_vol ~ prot_conc)
summary(model_linear)

slope <- summary(model_linear)$coefficients[2,1]
yint <- summary(model_linear)$coefficients[1,1]

# (4) Find x-intercept (Csat)...
# 0 = mx + c ... x = -c/m
Csat <- round(-yint/slope,2)

plt_Csat <- 
ggplot(data = df, mapping = aes(x = Protein_Conc_uM, y = Cond_Vol_in_sample_nL)) +
   theme(text = element_text(size=20)) +
   geom_point() +
   labs(title = "SFPQ(QG)-mEGFP condensation",
        subtitle = "100 mM KCl, 20 mM HEPES pH 7.4\n(room temperature)") +
   xlab(expression(paste("Total protein concentration (", mu, "M)", sep = ""))) +
   ylab("Condensed volume (nL)") +
   theme(plot.title = element_text(size = 20, face = "bold.italic"),
         plot.subtitle = element_text(size = 14, face = "italic"),
         axis.title.x = element_text(size = 17),
         axis.title.y = element_text(size = 17)) +
   stat_function(data = df_trunc, fun = function(prot_conc) slope*prot_conc + yint) +
   ylim(0, max(df_trunc$Cond_Vol_in_sample_nL)) +
   geom_segment(aes(x = Csat, 
                    y = 0, 
                    xend = Csat,
                    yend = max(df_trunc$Cond_Vol_in_sample_nL)/2),
                linetype = "dashed") +
   geom_label(
      label = paste("C(sat) = ", Csat, " uM", sep = ""),
      x = Csat,
      y = max(df_trunc$Cond_Vol_in_sample_nL)/2,
      size = 6,
      colour = "darkred") +
   theme(aspect.ratio=0.6)

plt_Csat

```

### 5. Calculate [protein] within condensed phase:

```{r}
### USER INPUT: ###
   # Total volume (in nL) of each sample here:
   sample_vol_nL <- 18

   # Protein MW (in Daltons):
   prot_mw <- 54737
   
### (end user input) ###


c_tot <- df_trunc$Protein_Conc_uM*10^-6     # <-Total [protein] (M)
v_tot <- sample_vol_nL*10^-6                # <-Sample Volume (L)

v_cond <- df_trunc$Cond_Vol_in_sample_nL*10^-9  # <-Condensed Vol (L)

c_dil <- Csat*10^-6                         # <-Dilute phase [protein] (M)
v_dil <- v_tot - v_cond                     # <-Dilute phase Vol (L)

# [protein] in condensed phase (c_cond) equals:
   # moles in the condensed phase (n_cond)
      # divided by
   # volume of condensed phase (v_cond)...
      
# Therefore, if
   # n_cond = n_tot - n_dil
   #        = c_tot*v_tot - c_dil*v_dil

# then,
   # c_cond = (c_tot*v_tot - c_dil*v_dil) / v_cond

# Calculate vector containing c_cond for each sample in df_trunc...
c_cond_M <- (c_tot*v_tot - c_dil*v_dil) / v_cond
c_cond_gL <- c_cond_M*prot_mw

# Append to df_trunc...
df_trunc$c_cond_M <- c_cond_M
df_trunc$c_cond_gL <- c_cond_gL

# Fit horizontal line...
model_c_cond <- nls(formula = c_cond_M ~ c_cond_M_fit,
                    data = df_trunc,
                    start = list(c_cond_M_fit=mean(df_trunc$c_cond_M)))
summary(model_c_cond)

c_cond_M_fit <- summary(model_c_cond)$coefficients[1,1]
c_cond_gL_fit <- c_cond_M_fit*prot_mw

ggplot(data = df_trunc, mapping = aes(x = Protein_Conc_uM, y = c_cond_M)) +
   theme(text = element_text(size=20)) +
   geom_point() +
   stat_function(fun = function(Protein_Conc_uM) c_cond_M_fit) +
   scale_y_continuous(
      name = "protein concentration (M)",
      sec.axis = sec_axis(trans = ~.*prot_mw, name = "mg/mL"),
      limits = c(0, max(c_cond_M))) +
   labs(title = paste("[protein] in condensed phase is ~ ", round(c_cond_gL_fit), " mg/mL", sep = "")) +
   xlab(expression(paste("Total protein concentration (", mu, "M)", sep = ""))) +
   theme(plot.title = element_text(size = 18, face = "bold.italic"),
         axis.title.x = element_text(size = 17),
         axis.title.y = element_text(size = 17)) +
   theme(aspect.ratio=0.6)

```

