---
title: "Calculate Csat (centrifuge)"
subtitle: "Data = 20210715_sfpqQG_150mMKCl"
author: "Andrew Marshall"
date: "19/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview:

This program:

1. Reads data collected using centrifuge approach for protein saturation concentration determination (supernatant A280 readings) **

2. Converts A280 to [protein] and plots supernatant [protein] over the total protein concentration

3. Fits a horizontal line to points at [protein] > saturation concentration **

4. Calculates saturation concentration (Csat = y-intercept)


\*\*Steps 1 and 3 require *user input*. 

### 1. Get data:

```{r get data}
### USER input: ###
   # protein extinction coefficient:
   extcoeff <- 0.481
   extcoeff_units <- "L/g"
   
   # protein molecular weight (Da):
   MW <- 103329.03
   
   # path to data (csv file):
   results_dir <- "\\\\uniwa.uwa.edu.au\\userhome\\staff7\\00101127\\My Documents\\LLPS results\\centrifuge_assays\\"
   results_data <- "20210715_sfpqQG_150mMKCl.csv"
   
   # Data points to exclude (e.g. pipetting errors)?:
      #(must be a vector)
   excluded <- c(13)
   
### (end user input) ###

# Reads in data: 
df <- read.csv(paste(results_dir, results_data, sep = ""))

# Excludes points from data (user-specified... e.g. known pipetting errors):
if (length(excluded) >= 1) {
   df_trunc <- df[-excluded,]
} else {
   df_trunc <- df
}
   
# Converts A280 to [protein] (micromolar):
sn_protein_gL <- df_trunc$A280/extcoeff
sn_protein_uM <- sn_protein_gL/MW*10^6
df_trunc$sn_protein_uM <- sn_protein_uM

```

### 2. Plot data:
```{r}
library(ggplot2)

ggplot(data = df_trunc, mapping = aes(x = sample_uM, y = sn_protein_uM)) +
   geom_point() +
   labs(title = "20210715_sfpqQG_(150mM KCl)")
```

### Conclusions...
Need to go to higher [protein]
