---
title: "Calculate Csat (centrifuge)"
subtitle: "Data = sfpqQG_CsatSN_data.csv"
author: "Andrew Marshall"
date: "04/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview:

This program:

1. Reads data collected using centrifuge method for protein saturation concentration determination (supernatant A280 readings) **

2. Converts A280 to [protein] and plots supernatant [protein] over the total protein concentration

3. Fits a horizontal line to points at [protein] > saturation concentration **

4. Calculates saturation concentration (Csat = y-intercept)


\*\*Steps 1 and 3 require *user input*. 

### 1. Get data:

```{r get data}
### USER input: ###
   # protein extinction coefficient:
   extcoeff <- 0.481
   extcoeff_units <- "L/g"
   
   # protein molecular weight (Da):
   MW <- 103329.03
   
   # path to data (csv file):
   results_dir <- "\\\\uniwa.uwa.edu.au\\userhome\\staff7\\00101127\\My Documents\\LLPS results\\centrifuge_assays\\"
   results_data <- "sfpqQG_CsatSN_data.csv"
   
   # Data points to exclude (e.g. pipetting errors)?:
      #(must be a vector)
   excluded <- c()
   
### (end user input) ###

# Reads in data: 
df <- read.csv(paste(results_dir, results_data, sep = ""))

# Excludes points from data (user-specified... e.g. known pipetting errors):
if (length(excluded) >= 1) {
   df_trunc <- df[-excluded,]
} else {
   df_trunc <- df
}

# Sort by KCl concentration and convert KCl_mM to factor:
df_trunc <- df_trunc[order(df_trunc$KCl_mM),]
df_trunc$KCl_mM <- as.factor(df_trunc$KCl_mM)

# Converts A280 to [protein] (micromolar):
sn_protein_gL <- df_trunc$A280/extcoeff
sn_protein_uM <- sn_protein_gL/MW*10^6
df_trunc$sn_protein_uM <- sn_protein_uM

# # Split data into different KCl concentrations:
# KCl500 <- df_trunc$KCl_mM == 500
# KCl500 <- df_trunc[KCl500,]
# KCl150 <- df_trunc$KCl_mM == 150
# KCl150 <- df_trunc[KCl150,]
# KCl100 <- df_trunc$KCl_mM == 100
# KCl100 <- df_trunc[KCl100,]
# KCl075 <- df_trunc$KCl_mM == 75
# KCl075 <- df_trunc[KCl075,]

```

### 2. Plot data:
```{r}
library(ggplot2)

ggplot(data = df_trunc, mapping = aes(x = sample_uM, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(method = "lm", formula = y ~ x) +
   xlim(0, 35) +
   ylim(0, 28)

# ggplot(data = KCl500, mapping = aes(x = sample_uM, y = sn_protein_uM)) +
#    geom_point() +
#    geom_point(data=KCl150, colour='blue') +
#    geom_point(data=KCl100, colour='green') +
#    geom_point(data=KCl075, colour='red') +
#    labs(title = "sfpqQG") +
#    xlim(0, 35) +
#    ylim(0, 28)
```

### Data Correction
```{r}
# Rationale: all input sample concentrations ('sample_uM') are calculated using 
# stock concentration divided by dilution factor. Stock concentration is very
# high and liable to be in error as it is in the high range of the nanodrop
# detection limit... this is likely to explain any deviation from 1.0 in 
# slope of protein dilution series in storage (high salt) buffer...

# Remove data points outside of concentration range of interest:
trimmer <- df_trunc$sample_uM < 15
df_trunc2 <- df_trunc[trimmer,]

# Fit straight line to 500mM data (slope should equal 1:
KCl500 <- df_trunc2$KCl_mM == 500
KCl500 <- df_trunc2[KCl500,]

lm500 <- lm(data = KCl500, formula = sn_protein_uM ~ sample_uM + 0)
slope500 <- lm500$coefficients[1]

# Multiply all sample_uM data by the slope of the fit to 500mM data (this should be 1)
df_trunc2$sample_uM_corrected <- df_trunc2$sample_uM*slope500


```


### 4. Plot Corrected data:
```{r}
library(ggplot2)

ggplot(data = df_trunc2, mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(method = "lm", formula = y ~ x+0) +
   xlim(0, 35) +
   ylim(0, 28)

```
### Calculate Csat for each [KCl] and indicate on plot:
```{r}
# Get all 500mM KCl data:
get500 <- df_trunc2$KCl_mM == 500
df_trunc2_500 <- df_trunc2[get500,]


# For datapoints with sample_uM_corrected > estimated Csat, calculate average 
# of all sn_protein_uM values (grouped by [KCl]):
get150overCsat <- df_trunc2$KCl_mM == 150 & df_trunc2$sample_uM_corrected > 10
df_trunc2_150overCsat <- df_trunc2[get150overCsat,]
Csat150 <- mean(df_trunc2_150overCsat$sn_protein_uM)

get100overCsat <- df_trunc2$KCl_mM == 100 & df_trunc2$sample_uM_corrected > 3
df_trunc2_100overCsat <- df_trunc2[get100overCsat,]
Csat100 <- mean(df_trunc2_100overCsat$sn_protein_uM)

get075overCsat <- df_trunc2$KCl_mM == 75 & df_trunc2$sample_uM_corrected > 1
df_trunc2_075overCsat <- df_trunc2[get075overCsat,]
Csat075 <- mean(df_trunc2_075overCsat$sn_protein_uM)


# library(dplyr)

ggplot(data = df_trunc2, mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(data = df_trunc2_500, method = "lm", formula = y ~ x+0, se = FALSE) +
   geom_hline(yintercept = Csat150, linetype = "dashed") +
   geom_hline(yintercept = Csat100, linetype = "dashed") +
   geom_hline(yintercept = Csat075, linetype = "dashed") +
   xlim(0, 35) +
   ylim(0, 28)

```

### Plot only 100mM and 500mM (control) data: 
```{r}
get100 <- df_trunc2$KCl_mM == 100
df_trunc2_100 <- df_trunc2[get100,]

# Convert Csat100 to string:
Csat100chr <- paste(round(Csat100, digits = 1), "\u03bcM")

ggplot(data = rbind(df_trunc2_500, df_trunc2_100), mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, group = KCl_mM)) +
   labs(title = expression(SFPQ(QG)~italic(C)[sat]~by~centrifugation)) +
   xlab("total [protein] (\u03bcM)") +
   ylab("supernatant [protein] (\u03bcM)") +
   scale_x_continuous(expand = c(0, 0.1)) + 
   scale_y_continuous(expand = c(0, 0.1)) +
   geom_point(aes(shape = KCl_mM), size = 2) +
   scale_shape_manual(values=c(1, 16),
                      name = "[KCl] (mM)") +
   geom_smooth(data = df_trunc2_500, method = "lm", formula = y ~ x+0, se = FALSE, colour = "black") +
   geom_segment(aes(x = 0, xend = max(df_trunc2_100$sample_uM_corrected), y = Csat100, yend = Csat100), linetype = "dashed") +
   annotate(
      "text",
      x = max(df_trunc2$sample_uM_corrected)*0.85,
      y = Csat100*0.7,
      size = 4,
      label = as.expression(bquote(bold(bolditalic(C)[sat] == .(Csat100chr))))) +
   theme_classic()
   
```



### Conclusions...

