---
title: "Calculate Csat (centrifuge)"
subtitle: "Data = sfpqWT_CsatSN_data.csv"
author: "Andrew Marshall"
date: "25/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview:

This program:

1. Reads data collected using centrifuge method for protein saturation 
concentration determination. Converts supernatant A280 readings to [protein]. **

2. Plots supernatant [protein] over the total protein concentration.

3. Adjusts [protein] values (within user-defined concentration range of interest)
to correct for non-linearity in nanodrop A280 readings. **

4. Calculates saturation concentration (Csat) by taking mean supernatant [protein] 
of points with total [protein] greater than user-estimated Csat. **

5. Plots horizontal line(s) to indicate Csat.


\*\*Steps 1, 3 and 4 require **user input**. 

### 1. Get data and calculate [protein]

```{r get data}
########################
### USER input: ########
   # protein extinction coefficient:
   extcoeff <- 0.473
   extcoeff_units <- "L/g"
   
   # protein molecular weight (Da):
   MW <- 105106
   
   # path to data (csv file):
   results_dir <- "\\\\uniwa.uwa.edu.au\\userhome\\staff7\\00101127\\My Documents\\LLPS results\\centrifuge_assays\\"
   results_data <- "sfpqWT_CsatSN_data.csv"
   
   # Exclude data from serial dilutions (TRUE or FALSE)?
   exclude_serial <- TRUE
   
   # Other data points to exclude (e.g. pipetting errors)?:
      #(must be a vector)
   excluded <- c()
   
### (end user input) ###
########################
   
# Reads in data: 
df <- read.csv(paste(results_dir, results_data, sep = ""))

# Excludes points from data (user-specified... e.g. known pipetting errors):
if (length(excluded) >= 1) {
   df_trunc <- df[-excluded,]
} else {
   df_trunc <- df
}

# Sort by KCl concentration and convert KCl_mM to factor:
df_trunc <- df_trunc[order(df_trunc$KCl_mM),]
df_trunc$KCl_mM <- as.factor(df_trunc$KCl_mM)

# Converts A280 to [protein] (micromolar):
sn_protein_gL <- df_trunc$A280/extcoeff
sn_protein_uM <- sn_protein_gL/MW*10^6
df_trunc$sn_protein_uM <- sn_protein_uM

```

### 2. Plot data
```{r}
library(ggplot2)

ggplot(data = df_trunc, mapping = aes(x = sample_uM, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(method = "lm", formula = y ~ x+0) 
   # xlim(0, 35) +
   # ylim(0, 28)

```

### 3. Data Correction
```{r}
# Rationale: all input sample concentrations ('sample_uM') are calculated using 
# stock concentration divided by dilution factor. Stock concentration is very
# high and liable to be in error as it is in the high range of the nanodrop
# detection limit... this is likely to explain any deviation from 1.0 in 
# slope of protein dilution series in storage (high salt) buffer...

########################
### USER input: ########
   # Remove data points outside of concentration range of interest:
   trimmer <- df_trunc$sample_uM < 50
   df_trunc2 <- df_trunc[trimmer,]
### (end user input) ###
########################

if (exclude_serial == TRUE) {
   # Remove data fom SERIAL DILUTIONS:
   trimmer <- df_trunc2$dilution_type == "direct"
   df_trunc2 <- df_trunc2[trimmer,]
}

# Fit straight line to 500mM data (slope should equal 1:
KCl500 <- df_trunc2$KCl_mM == 500
KCl500 <- df_trunc2[KCl500,]

lm500 <- lm(data = KCl500, formula = sn_protein_uM ~ sample_uM + 0)
slope500 <- lm500$coefficients[1]

# Multiply all sample_uM data by the slope of the fit to 500mM data (this should be 1)
df_trunc2$sample_uM_corrected <- df_trunc2$sample_uM*slope500

```

## *Correction factor = `r slope500`*
(All [protein] values are multiplied by this)

#### ... plot trimmed and corrected data:
```{r}
library(ggplot2)

ggplot(data = df_trunc2, mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point()

```

### 4. Calculate Csat for each [KCl] and indicate on plot
```{r}
# Get all 500mM KCl data:
get500 <- df_trunc2$KCl_mM == 500
df_trunc2_500 <- df_trunc2[get500,]

########################
### USER input: ########
   # For datapoints with sample_uM_corrected > estimated Csat, calculate average 
   # of all sn_protein_uM values (grouped by [KCl]):
   get150overCsat <- df_trunc2$KCl_mM == 150 & df_trunc2$sample_uM_corrected > 20
   df_trunc2_150overCsat <- df_trunc2[get150overCsat,]
   Csat150 <- mean(df_trunc2_150overCsat$sn_protein_uM)
   Csat150sd <- sd(df_trunc2_150overCsat$sn_protein_uM)
   
   get100overCsat <- df_trunc2$KCl_mM == 100 & df_trunc2$sample_uM_corrected > 10
   df_trunc2_100overCsat <- df_trunc2[get100overCsat,]
   Csat100 <- mean(df_trunc2_100overCsat$sn_protein_uM)
   Csat100sd <- sd(df_trunc2_100overCsat$sn_protein_uM)
   
   get075overCsat <- df_trunc2$KCl_mM == 75 & df_trunc2$sample_uM_corrected > 3
   df_trunc2_075overCsat <- df_trunc2[get075overCsat,]
   Csat075 <- mean(df_trunc2_075overCsat$sn_protein_uM)
   Csat075sd <- sd(df_trunc2_075overCsat$sn_protein_uM)
### (end user input) ###
########################

# library(dplyr)

ggplot(data = df_trunc2, mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, shape = KCl_mM)) +
   geom_point() +
   geom_smooth(data = df_trunc2_500, method = "lm", formula = y ~ x+0, se = FALSE) +
   geom_hline(yintercept = Csat150, linetype = "dashed") +
   geom_hline(yintercept = Csat100, linetype = "dashed") +
   geom_hline(yintercept = Csat075, linetype = "dashed")
   # xlim(0, 35) +
   # ylim(0, 28)

```

### Plot only 100mM and 500mM (control) data: 
```{r}
get100 <- df_trunc2$KCl_mM == 100
df_trunc2_100 <- df_trunc2[get100,]

# Convert Csat100 to string:
Csat100chr <- paste(round(Csat100, digits = 1), "\u00b1", round(Csat100sd, digits = 1), "\u03bcM")

ggplot(data = rbind(df_trunc2_500, df_trunc2_100), mapping = aes(x = sample_uM_corrected, y = sn_protein_uM, group = KCl_mM)) +
   labs(title = expression(SFPQ(WT)~italic(C)[sat]~by~centrifugation), caption = paste("Uncertainty expressed as SD. [protein] correction factor =",round(slope500, digits = 3))) +
   xlab("total [protein] (\u03bcM)") +
   ylab("supernatant [protein] (\u03bcM)") +
   scale_x_continuous(expand = c(0, 0.1)) + 
   scale_y_continuous(expand = c(0, 0.1)) +
   geom_point(aes(shape = KCl_mM), size = 1.5) +
   scale_shape_manual(values=c(1, 16),
                      name = "[KCl] (mM)") +
   geom_smooth(data = df_trunc2_500, method = "lm", formula = y ~ x+0, se = FALSE, colour = "black", size = 0.5) +
   geom_segment(aes(x = 0, xend = max(df_trunc2_100$sample_uM_corrected), y = Csat100, yend = Csat100), linetype = "dashed") +
   annotate(
      "text",
      x = max(df_trunc2$sample_uM_corrected)*0.75,
      y = Csat100*0.6,
      size = 3,
      label = as.expression(bquote(bold(bolditalic(C)[sat] == .(Csat100chr))))) +
   theme_classic(base_size = 9) +
   theme(legend.key.size = unit(4, "mm"),
         legend.title = element_text(size = 7),
         legend.text = element_text(size = 6),
         legend.position = c(0.15,0.85),
         aspect.ratio = 1,
         plot.caption = element_text(size = 5, colour = "darkgrey")
         )


   
```



### Save plot to file:
```{r}
ggsave(filename = "sfpqWT_CsatSN_100mM_Rplot8x8_300.png", 
       plot = last_plot(), 
       device = "png", 
       path = results_dir, 
       scale = 1,
       width = 8,
       height = 8,
       units = "cm",
       dpi = 300,
       limitsize = TRUE,
       bg = NULL)
```



### Conclusions...

